Injury Outcomes

### 2023-08-18 injury_tables.Rmd
updated injury and PA/AP output calculations

# WARNING: Script assumes that the Baseline scenario corresponds to the known injury fatality counts in the city, i.e. 
#          it assumes that the reference scenario is the Baseline scenario

@@

```{r}
# Export injury datasets in a single excel sheet
path_inj_wb <- "results/multi_city/inj/inj_data.xlsx"
 writexl::write_xlsx(list(inj_counts = inj_counts_list, #%>% filter(str_mode != 'Total'),
                          injury_risks_billion_kms = rd,
                          injury_risks_100k_people  = injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'),
                          injury_risks_100mil_h = rd_hours,
                          true_distances = true_distances_df),
                     path = path_inj_wb)
```

>>>>

# WARNING: Script assumes that the Baseline scenario corresponds to the known injury fatality counts in the city, i.e it assumes that the reference scenario is the Baseline scenario

@@

```{r}
# Export injury datasets in a single excel file
path_inj_wb <- "results/multi_city/inj/inj_data.xlsx"
 writexl::write_xlsx(list(inj_counts = inj_counts_list, #%>% filter(str_mode != 'Total'),
                          injury_risks_billion_kms = rd,
                          injury_risks_100k_people  = injury_risks_per_100k %>% filter(mode != 'Total' & scenario != 'Total'),
                          injury_risks_100mil_h = rd_hours,
                          true_distances = true_distances_df),
                     path = path_inj_wb)
```
